\section{Evaluation Metrics}

The utilized dataset contains ground truth sensor position and orientation along with two 
evaluation metrics: Absolute Trajectory Error (ATE) and Relative Pose Error (RPE). These metrics 
allows estimating local and global error of the estimations compared to the provided ground truth measure. The dataset
 also provides the necessary tools to calculate the metrics. A detailed explanation can be found in \cite{sturm12iros}.

We have a sequence of poses from estimated trajectory $P_1,P_2,...,P_n \in SE(3)$ and from ground truth trajectory 
$Q_1,Q_2,...,Q_n \in SE(3)$. Each pose represents global rotation and translation of the sensor.



\subsection{Relative Pose Error}

This error measure compares the ground truth sensor trajectory in a fixed interval of time, frames, distance or degrees. 
Allowing for example to estimate how much error is produced frame to frame.

The relative pose error at time $i$ is defined as follows:

\begin{equation}
E_i = ( Q_i^{-1} Q_{i+\Delta})^{-1}(P_i^{-1}P_{i+\Delta})
\end{equation}

From these errors the Root Mean Squared Error (RMSE) is calculated over all time indices of the translational component as:

\begin{equation}
VRMSE(E_{1:n},\Delta) = (\frac{1}{m} \sum_{i=1}^m ||trans(E_i)||^2 )^{\frac{1}{2}}
\end{equation}


\subsection{Absolute Trajectory Error}

This error measure compares the ground truth sensor trajectory with the proposed trajectory using root mean 
squared error and considering only translational errors. It is not necessary to consider the rotational components, 
because they are implicitly affecting successive sensor translations.

Since both trajectories can be in different coordinate frames, first they are aligned using the Horn method \cite{Horn}. If $S$ 
is the rigid-body transformation (obtained by least squares) that maps $P_{1:n}$ to $Q_{1:n}$, the absolute trajectory error
 at time step $i$ can be defined as follows:

\begin{equation}
F_i=Q_i^{-1}SP_i
\end{equation}

Then the root mean squared error over all time indices of the translational components can be defined as:

\begin{equation}
RMSE(F_{1:n}) = (\frac{1}{n} \sum_{i=1}^n ||trans(F_i)||^2 )^{\frac{1}{2}}
\end{equation}





