
\section{Iterative Closest Point}

The ICP algorithm \cite{mckay92} is widely used for 3D reconstruction. This algorithm tries to find 
the optimal rotation and translation between two point clouds that minimizes the distance between corresponding 
points. Corresponding points are determined assigning to each point of one cloud, the closest point in the other cloud.

As result at each iteration we have a set of pairs of the closest points, where each pair contains one point of each cloud. This set 
of pairs changes from iteration to iteration, since the rotation and translation updates the points of one of the point clouds. If enough correct 
corresponding points are found in each iteration, the algorithm converges to the correct transformation that aligns both point clouds.


\begin{itemize}
\item $R$ : $3\times3$ Rotation matrix
\item $t$ : $3\times1$ Translation vector
\item $srcPointCloud,srcPointCloud',tgtPointCloud$ : Point sets $\in R^3$
\item $pointPairs$ : Pair set
\end{itemize}
%\small
\begin{algorithm}
\caption{ICP algorithm}
\begin{algorithmic}[1]
\State init(R,t)
\State srcPointCloud' $\leftarrow$ transform(srcPointCloud,R,t) 
\State pointPairs $\leftarrow$ closestPoints(srcPointCloud',tgtPointCloud)
\State $\{R,t\} \gets$ updateTransformation(pointPairs)
\State $e_i = meanSquareError(p)$
\If {$e_i < threshold$ OR  $i > maxIteracions$} 
	\State return R,t
\Else
	\State go to step 2
\EndIf
\end{algorithmic}
\end{algorithm}


We want to find R and t that minimizes the following expression:

$$ \sum\limits_{i=1}^n ||R a_i -  b_i - t ||^2 \ ,$$

\noindent where each $a_i,b_i$ is a vector $\in \mathbb{R}^3$, R is a $3\times3$ rotation matrix and t is a vector $\in \mathbb{R}^3$


We make a change of coordinates, placing the centroid of each cloud as origin:



\begin{align*}
 \bar{a} = \frac{1}{n} \sum\limits_{i=1}^n {a_i} \ ,\\ 
  \bar{b} = \frac{1}{n} \sum\limits_{i=1}^n {b_i} \ , \\  
   {a'}_i = a_i - \bar{a} \ , \\
   {b'}_i = b_i - \bar{b} \ ,
\end{align*}

\noindent replacing:

\[ \sum\limits_{i=1}^n ||R a_i -  b_i - t ||^2 = \sum\limits_{i=1}^n ||R ( {a'}_i + \bar{a} ) -  ( {b'}_i  + \bar{b} ) - t ||^2  \ . \] 

\noindent The desired translation is $t = R \bar{a} - \bar{b} $. We must consider the rotation in this expression, since 
the rotation of a point cloud will change the position of all points and as consequence the translation.

Replacing $t$ in our previous expression we get:
\begin{flalign*}
&\sum\limits_{i=1}^n ||R a'_i - b'_i ||^2  \ , \\ 
&=\sum\limits_{i=1}^n (R a'_i - b'_i)^t (R a'_i - b'_i) \ , \\
&=\sum\limits_{i=1}^n ( (R a'_i)^t R a'_i - (R a'_i)^t b'_i  - b_i^{\prime t} R a'_i + b_i^{\prime t} b'_i) \ , \\
&=\sum\limits_{i=1}^n ( a_i^{\prime t} R^t R a'_i - 2 b_i^{\prime t} R a'_i + b_i^{\prime t} b'_i) \ , \\ 
&=\sum\limits_{i=1}^n (a_i^{\prime t} a'_i -  2 b_i^{\prime t} R a'_i + b_i^{\prime t} b'_i) \ .
\end{flalign*}


\noindent Minimize the previous expression is equivalent to maximize:

\begin{align*}
& \sum\limits_{i=1}^n b_i^{\prime t} R a'_i =  Trace ( \sum\limits_{i=1}^n R a'_i  b_i^{\prime t} ) = Trace (RH) \ ,\\
& H=\sum\limits_{i=1}^n a'_i  b_i^{\prime t} \ . 
\end{align*}


Lemma (\ref{ap:lemma}): For any positive definite matrix $A A^t$ and any orthogonal matrix B

\[ Trace( A A^t ) \geq Trace (B A A^t) \ . \]


\noindent Now using this lemma we will maximize our expression:


Let's apply the SVD factorization to H, then:

\[ H = U \Sigma V^t \ , \]

\noindent where U and V are $3\times3$ orthonormal matrices and $\Sigma$ is a diagonal matrix with no negative elements.

Let $ R = V U^t $ then :

\begin{align*}
RH = VU^t U \Sigma V^t = V \Sigma V^t = V \Sigma^{\frac{1}{2}} (V \Sigma^{\frac{1}{2}})^t \ ,
\end{align*}

\noindent which is symmetrical and positive definite.
Therefore, from lemma, for any $3\times3$ orthonormal matrix B :

\[ Trace( R H ) \geq Trace( B R H ) \ . \]

Thus, the solution for our problem is :

\begin{align*}
R = V U^t \ , \\
t = R \bar{a} - \bar{b} \ .
\end{align*}


\noindent This means that if we apply the rotation $R$ and the translation $t$, to each point of the point cloud A, the distance between the
 closest points of 
transformed point cloud A with point cloud B will be minimal, when registering a set of points from a real 3D scene it allows aligning 
successive scene frames.
