\section{Photo-consistency}
\label{sec:photocons}

Having an estimation of rotation R and translation $t$ to align source point cloud with target point cloud, 
it is possible to re-project the 3D points to the 2D image plane using the 
camera parameters. If we have a point $p=(X,Y,Z)$ we can project it to the image plane using the following formula obtained 
from the pinhole camera model:

\begin{equation}
U(p) = (\frac{fX}{Z} - c_x, \frac{fY}{Z} - c_y) \ ,
\label{eq:reproject}
\end{equation}

\noindent where $f$ and $(c_x,c_y)$ denote the focal length and optical center of the pinhole camera model. 
We can apply the transformation $R,t$ to the point before projecting it:

\begin{equation}
T(R,t,p) = Rp + t = p' \ .
\end{equation}

\noindent Image coordinates  $U(p')$ are used to obtain image color in the target image, making a re-projection of $p'$ to the image plane.

Then we can apply the following error formula, that represents the color differences between the re-projected image and 
the target image. 

\begin{equation}
E(R,t) = \frac{1}{N} \sum\limits_{p\ \in\ C_s} |I_s(U(p)) - I_t(U(p'))| \ ,
\end{equation}


\noindent where:
\begin{itemize}
\item N is the number of points.
\item $U(p)$ is the re-projection function \ref{eq:reproject} that returns $(x,y)$ image coordinates of an $(X,Y,Z)$ point.
\item  $I_s(x,y)$ is function that returns a vector $(R,G,B)$ representing image color at location $(x,y)$. Where 
R,G,B are positive integers between 0 and 255. The same holds for $I_t(x,y)$. Both functions represent 
source and target images respectively.
\item $C_S$ is the source point cloud.
\item When applying the formula it must be verified that $I_t(U(p'))$ is valid.
\end{itemize}

In this case the average color difference vector norm is used, but there are many ways of measure photo-consistency, 
for example using a color space different from RGB or using another error metric. Photo-consistency is widely used in 3D reconstruction, for example some works using it are \cite{Whelan13},\cite{kerl13icra} and \cite{Newcombe10livedense}.

